---
title: "hw0"
author: "HarperLiang"
format: html
editor: visual
execute: 
  echo: false
---

#### 1. Write a Quarto document that defines variables $a=1, b=3, c=2$ and print out the solutions to $f(x) = ax^2 + bx + c = 0$. Do not report complex solutions, only real numbers.

We would like to find a solution to quadratic function of the form $ax^2 + bx + c = 0$. In the first step, we calculate the discriminant (denoted as 'dis'), using the formula $\Delta = b^2 - 4ac$. The solution of the quadratic equation depends on the sign of the discriminant $\Delta$, which leads to three possible cases:

1.  If $\Delta > 0$, then the quadratic equation has two solutions: $x = \frac{-b-\sqrt{\Delta}}{2a}$ and $x = \frac{-b + \sqrt{\Delta}}{2a}$

2.  If $\Delta=0$, then the quadratic equation has one solution: $x=\frac{-b}{2a}$

3.  If $\Delta<0$, then the quadratic equation f(x) has no real solution.

    In this case, the discriminant is larger than 0, and the equation has 2 solutions.

```{r}
fn<-function(a,b,c){
  dis = b^2 - 4*a*c
  if (dis > 0){
    x_1 = (-b + sqrt(dis))/(2*a)
    x_2 = (-b - sqrt(dis))/(2*a)
    return (paste0("The solutions for f(x) are ", c(x_1), " and ", c(x_2)))
  }
else if (dis == 0){
  x = -b /(2*a)
  return (x)
}
  else {
    return("f(x) has no real solution.")
  }
}
```

```{r}
#fn(a = 1, b = -1, c = -2)
#fn(a = 1, b = 2, c = 5)
fn(a = 1, b = 3, c = 2)
```

#### 2. Include a graph f(x)

The domain over which we want to plot f(x) is (-5,5). And then we plot f(x) and the line y = 0. The plot can confirm the results -1 and -2.

```{r}
a <- 1 
b <- 3
c <- 2
x <- seq(-5, 5, length = 300)
plot(x, a*x^2 + b*x + c, type = "l")
abline(h = 0, lty = 2)
```
